Quantum Pseudo-Telepathy

### 2023-06-22 paper/main.tex
Proof product rows and columns (without figure)

\paragraph{Outline of this paper.}
\section{Contextuality}
\label{sec:local-context}

@@

{\renewcommand{\arraystretch}{2}
\begin{figure}
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = -\ci{}I \otimes \ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = \ci{}I \otimes \ci{}I = -I}
    \end{array}\]
  \caption{\label{fig:quantum}}
\end{figure}}

@@

\section{Quantum Unitaries (? research)}
\label{sec:quantum-unitaries}

>>>>

\paragraph{Outline of this paper.}

@@

{\renewcommand{\arraystretch}{2}
\begin{figure}
  \centering
  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
      \hhline{---~}
      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
      \\ \hhline{---~}
      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
      \\ \hhline{---~}
      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
      \\ \hhline{---~}
      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
    \end{array}\]
  \caption{\label{fig:quantum}}
\end{figure}}

@@

\subsection{Formal Proof}
To prove that the quantum solution indeed works, we must demonstrate
two fundamental properties. First, the product of the outcomes of the
three measurements on each row (equivalently, column) is equal to 1
(equiv. -1). Second, the outcome of Alice's measurements on the
intersection is always equal to the outcome of Bob's
measurement. Lemma~\ref{lem:product} formalizes the product property.

\begin{lemma}[The Product Property of the Quantum Solution]
  \label{lem:product}
  Let \(M_{i, j}\) be the observable at the cell \((i, j)\) of the
  \(3 \times 3\) grid shown in Figure~\ref{fig:quantum}. Then,
  it follows that

  \begin{align}
    \textit{for every }i, \prod_{j} \operatorname{Out}(M_{i, j}) &= +1  \textit{, and} \\
    \textit{for every }j, \prod_{i} \operatorname{Out}(M_{i, j}) &= -1.
  \end{align}
\end{lemma}

\begin{proof}
  \label{proof:product}
  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\) and
  \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and, similarly,
  \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these properties, we can see
  that the product of every row (equiv. column) is the identity \(I\)
  (equiv. \(-I\)), regardless of the order of the three observables.
  That is, the three observables of every row and every column
  mutually commute (or, in other words, they are compatible).
  Consequently, for every row and every column, it is possible to find
  a basis of eigenvectors that are common to the three observables,
  meaning that they can be simultaneous
  diagonalized. Figure~\ref{fig:eigenv} shows these common
  eigenvectors. Let  \(M_{i, j}\) be the observables at each cell.
  Then, for every row \(i\) (equiv. column \(j\)), we have
  \begin{align}
    M_{i, 0} M_{i, 1} M_{i, 2}
    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
      \nonumber \\
    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
    &= P_{i}\Lambda_{i}P_{i}^{-1},
  \end{align}
  where \(P_{i}\) is the matrix whose columns are the common
  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
  formed by the products of the eigenvalues of the observables,
  associated with the same eigenvector. What this essentially means is
  that any measurement \(M_{i, j}\) yields one of the eigenvalues
  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and collapses the
  state to a linear combination of one of the two shared eigenvectors
  \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
  \(\lambda\)-eigenspace. Then, the second measurement will collapse
  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\).
  Consequently, the third measurement will not change the state any
  further. Therefore, the product of the three outcomes will be the
  product of the eigenvalues associated with either
  \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\), which is one of the
  entries in the diagonal of \(\Lambda_{i}\). But, notice that
  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
  the only possible value for the product is \(1\) (equiv. \(-1\) for
  columns).
\end{proof}

\section{Quantum Unitaries (? research)}
\label{sec:quantum-unitaries}

\section{Contextuality}
\label{sec:context}
